FantasticLamp: a genome graph based pipeline for calculating the efficacy of genomic edits

### 2023-08-03 paper/main.tex
...

The initial development and testing of this pipeline were carried out using a dataset containing sequencing reads from various experiments. These experiments involved multiple alterations - insertions, deletions, and substitutions - on a population of \textit{Saccharomyces cerevisiae}. They were performed in distinct batches by Inscripta Inc. (reference pending).

@@

This synthetic dataset encompassed a small reference genome, a related design library CSV, which contained both the reference and edited sequences from the genome, and artificial reads mapping to either the reference or the edit at a specific edit locus. 
Notably, the pipeline was successful in accurately calculating the edit coverage from this dataset, providing a quantitative evaluation of the edit's effectiveness.

>>>>

The initial development and testing of this pipeline were carried out using a dataset containing sequencing reads from various experiments.
These experiments involved multiple alterations---insertions, deletions, and substitutions---on a population of \textit{Saccharomyces cerevisiae}.
They were performed in distinct batches by Inscripta Inc. \cite{gander2021simultaneous}.

@@

This synthetic dataset encompasses a small reference genome, a related design library CSV, which contain both the reference and edited sequences from the genome, and artificial reads mapping to either the reference or the edit at a specific edit locus. 
\textit{FantasticLamp} accurately calculated the edit coverage from this dataset, providing a quantitative evaluation of the edit's effectiveness.
We provide this as a standard test in our code repository.
